|

### 2022-04-07 front-and-back-matter/99-appendices.Rmd
Corrections to front and back matter

<!----------------------------------------------------------------------------->
(ref:missingMatrix-caption) __Overview of missing data in the IPD analysis__ - Missing variables/values across cohorts included in the IPD analysis. Missing variables are denoted using a "-", while missing values are described as N (%). Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.

>>>>

<!----------------------------------------------------------------------------->
(ref:missingMatrix-caption) __Overview of missing data in the IPD analysis__ - Missing variables/values across cohorts included in the IPD analysis. Missing variables are denoted using a "-", while missing values are described as N (%). Note that [LDL-c]{.correction} is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, [HDL-c]{.correction} and TG following multiple imputation of missing values in these variables.

### 2022-04-07 front-and-back-matter/_abstract.Rmd
Corrections to front and back matter

__Background:__ Identification of causal relationships between modifiable risk factors and incidence of dementia is central to the development of evidence-based prevention strategies. [Blood lipids represent such a modifiable risk factor, though considerable uncertainty remains concerning their relationship with dementia outcomes.]{.correction} As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, [low-density-lipoprotein cholesterol (LDL-c), high-density-lipoprotein cholesterol (HDL-c)]{.correction}, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.

@@

__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across the study designs considered, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use. Analysis of the CPRD data provided [very]{.correction} weak evidence for [an effect of statins on Alzheimer's disease but suggested a harmful association with the all-cause, vascular and other dementia outcomes,]{.correction} likely due to confounding by indication. The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only [(Odds ratio: 1.25, 95%CI: 1.01-1.54)]{.correction}. Finally, the quantitative triangulation analysis did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.

>>>>

__Background:__ Identification of causal relationships between modifiable risk factors and incidence of dementia is central to the development of evidence-based prevention strategies. [While blood lipids represent an easily modifiable target for preventative intervention, the evidence for their relationship with dementia outcomes is inconclusive due to the set of contradictory results reported by previous studies]{.correction} As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, [low-density-lipoprotein cholesterol (LDL-c), high-density-lipoprotein cholesterol (HDL-c)]{.correction}, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.

@@

__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across the study designs considered, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use. Analysis of the CPRD data provided [very]{.correction} weak evidence for [an effect of statins on Alzheimer's disease but suggested a harmful association with the all-cause, vascular and other dementia outcomes,]{.correction} likely due to confounding by indication. The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only [(odds ratio: 1.25, 95%CI: 1.01-1.54)]{.correction}. Finally, the quantitative triangulation analysis did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
